\section{Methodology} \label{sec:methodology}

This report is grounded in both past and present research.

A literature review on traditional malware evasion forms the basis for the study's taxonomy and framework.
Studying these historical evasion techniques gives insights into potential trends for the blockchain ecosystem.

In addition to the lessons from the past, the study also incorporates findings from current research in the web3 space.
This research is sourced from academic papers, conferences, tools, and watch groups focused on blockchain security.

The report's practical aspect is backed by an analysis of selected smart contract samples.
These samples were chosen for two reasons: their association with recent hacks and their ability to slip past detection mechanisms, especially those of the \href{https://explorer.forta.network/}{Forta network}.
% Contracts from other platforms such as \href{https://www.chainabuse.com/reports}{chainabuse}, \href{https://www.web3rekt.com/}{web3rekt}, and \href{https://www.rekt.news/}{rekt.news} provided the necessary data for this analysis.

Forta being a network of independent scanning agents, each of them is free to implement a different approach.
Since it is not bound by a systemic choice of detection, the countermeasures are centered on each evasion technique.
Static, dynamic, hybrid, graph analysis are all mentioned when it is relevant to a given target.

The analysis is meant as a reference guide for the development of future bots on the Forta network.
It will be a continuous feeedback loop: the report will be updated regularly as progress is made.
