\section{Red-Pill} \label{sec:red-pill}

\subsection{Overview}

The red-pill technique detects simulation environment to disable its exploits upon scrutiny. 

The contract detects simulation environments by checking:

\begin{itemize}
\item{global variables: these variables may have special values in test environments
\begin{itemize}
    \item{\lstinline[language=Solidity]{block.basefee}: \lstinline{0}}
    \item{\lstinline[language=Solidity]{block.coinbase}: \lstinline{0x0000000000000000000000000000000000000000}}
    \item{\lstinline[language=Solidity]{tx.gasprice}: large numbers, higher than \lstinline{0xffffffffffffffff}}
\end{itemize}}
\item{other contracts: by probing third party contracts, it can assess whether the blockchain mainnet is available}
\end{itemize}

\subsection{Evasion Targets}

\subsubsection{Wallets}

Wallets often perform a simulation of the transaction before committing.
The whole point of this method is to pass these tests and bait the end-user.

\subsubsection{Security Tools}

Automatic tools will likely not fuzz the coinbase or other global variables.
So the dynamic analysis may follow the "harmless" branch and not inspect the actual behavior of the contract on the mainnet.

On the other hand these unusual checks stand out when reviewing the code.

\subsection{Samples}

The contract \lstinline{FakeWethGiveaway} mentioned in \href{\urlarticleredpill}{the Zengo article} checks the current block miner’s address:

\begin{lstlisting}[language=Solidity]
function checkCoinbase() private view returns (bool result) {
    assembly {
        result := eq(coinbase(), 0x0000000000000000000000000000000000000000)
    }
}
\end{lstlisting}

When null (test env), it actually sends a reward:

\begin{lstlisting}[language=Solidity]
bool shouldDoTransfer = checkCoinbase();
if (shouldDoTransfer) {
    IWETH(weth).transfer(msg.sender, IWETH(weth).balanceOf(address(this)));
}
\end{lstlisting}

Otherwise, on the mainnet, it just accepts transfers without doing anything.

\subsection{Detection \& Countermeasures}

\subsubsection{Control Flow Graph}

The flow of each function, especially the conditional jumps, can be parsed from the bytecode.
And further analyzed to find the conditional jumps that depend on the global variables mentioned above.

\subsubsection{Differential Testing}

Another approach is to use the historic transactions as invariants.
Replay them and fuzz the global variables with blank data, to see if it changes the behavior.

The transactions can be compared at a high level thanks to their gas consumption.
